State of the Practice for Lattice Boltzmann Method Software

### 2022-01-07 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
sorted LBM paper Table 4 by percent code comments

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3.5cm}p{3.5cm}p{3.5cm}p{2.5cm} }
			\toprule
			Name & $\%$ Issues Closed & $\%$ Code Comments & Status\\
			\midrule
			DL\_MESO (LBE) & Not Git & 8.06& Alive\\
			ESPResSo & 89.26 & 21.78 & Alive\\
			ESPResSo++ & 66.28 & 17.10 & Alive\\
			HemeLB & No Issues & 16.68 & Dead\\
			laboetie & 18.75 & 2.47 & Dead\\		
			LatBo.jl & 93.33 & 0.40 & Dead\\
			LB2D-Prime & Not Git & 13.61 & Dead\\
			LB3D & Not Git & 13.76 & Dead\\
			LB3D-Prime & Not Git & 14.34 & Dead\\
			lbmpy& 58.33  & 2.03 & Alive\\
			lettuce & 33.33 & 8.19 & Alive\\
			LIMBES & Not Git & 17.39 & Dead\\
			Ludwig& 60.00 & 20.70 & Alive\\
			LUMA& 85.71   & 0.20 & Alive\\
			MechSys & Not Git & 15.11 & Alive\\
			MP-LABS & 100.00 & 26.67 & Dead\\
			Musubi & Not Git & 24.19 & Alive\\
			OpenLB & Not Git & 22.43 & Alive\\
			Palabos & 89.47 & 17.76 & Alive\\
			pyLBM & 66.67& 16.12 & Alive\\
			Sailfish & 22.22 & 9.26 & Alive\\
			SunlightLB & Not Git & 17.67 & Dead\\
			TCLB & 60.32 & 6.02 & Alive\\
			waLBerla & 72.90 & 22.62 & Alive\\
			\bottomrule
		\end{tabular}
		\caption{Git Repository Data} \label{gitrepodata}
	\end{center}
	\end{table}

>>>>

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3.5cm}p{3.5cm}p{3.5cm}p{2.5cm} }
			\toprule
			Name & $\%$ Issues Closed & $\%$ Code Comments & Status\\
			\midrule
			MP-LABS & 100.00 & 26.67 & Dead\\
			Musubi & Not Git & 24.19 & Alive\\
			waLBerla & 72.90 & 22.62 & Alive\\
			OpenLB & Not Git & 22.43 & Alive\\
			ESPResSo & 89.26 & 21.78 & Alive\\
			Ludwig& 60.00 & 20.70 & Alive\\
			Palabos & 89.47 & 17.76 & Alive\\
			SunlightLB & Not Git & 17.67 & Dead\\
			LIMBES & Not Git & 17.39 & Dead\\
			ESPResSo++ & 66.28 & 17.10 & Alive\\
			HemeLB & No Issues & 16.68 & Dead\\
			pyLBM & 66.67& 16.12 & Alive\\
			MechSys & Not Git & 15.11 & Alive\\
			LB3D-Prime & Not Git & 14.34 & Dead\\
			LB3D & Not Git & 13.76 & Dead\\
			LB2D-Prime & Not Git & 13.61 & Dead\\
			Sailfish & 22.22 & 9.26 & Alive\\
			lettuce & 33.33 & 8.19 & Alive\\
			DL\_MESO (LBE) & Not Git & 8.06& Alive\\
			TCLB & 60.32 & 6.02 & Alive\\
			laboetie & 18.75 & 2.47 & Dead\\	
			lbmpy& 58.33  & 2.03 & Alive\\	
			LatBo.jl & 93.33 & 0.40 & Dead\\
			LUMA& 85.71   & 0.20 & Alive\\
			\bottomrule
		\end{tabular}
		\caption{Git Repository Data} \label{gitrepodata}
	\end{center}
	\end{table}
